---
title: "p8105_hw6_bh2849"
author: "Binyue Hu"
date: "2022-12-03"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

### Problem 2

#### Load and Tidy the Data

```{r message=FALSE}
homicides_data = read_csv("./data/homicide-data.csv")

homicides_data = homicides_data %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = "_")) %>% 
  filter(!city_state %in% c("Dallas_TX", "Phoenix_AZ", "Kansas City_MO", "Tulsa_AL"), 
         victim_race %in% c("Black", "White")) %>% 
  mutate(victim_age = as.numeric(victim_age),
         resolved = case_when(
           disposition == "Closed without arrest" ~ 0,
           disposition == "Open/No arrest" ~ 0,
           disposition == "Closed by arrest" ~ 1
         ))
```

### Fit Logistic Regression for Baltimore
```{r glm_baltimore}
baltimore_glm = homicides_data %>% 
  filter(city_state == "Baltimore_MD") %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, family = binomial(), data = .) %>% 
  broom::tidy() %>% 
  mutate(odds_ratio = exp(estimate),
         CI_lower = exp(estimate - 1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>% 
  filter(term == "victim_sexMale") %>%
  select(term, odds_ratio, CI_lower, CI_upper) 

baltimore_glm
```

### For All Cities
```{r glm_all}
cities_glm = homicides_data %>% 
  nest(cities = -city_state) %>%
  mutate(models = map(.x = cities, ~glm(resolved ~ victim_age + victim_sex + victim_race, family = binomial(), data = .)),
         results = map(models, broom::tidy)) %>% 
  select(-models, -cities) %>% 
  unnest(cols = results) %>% 
  mutate(odds_ratio = exp(estimate),
         CI_lower = exp(estimate - 1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, odds_ratio, CI_lower, CI_upper)

cities_glm
```

### Plot for adjusted OR and 95% CI
```{r plot_or}
or_plot = cities_glm %>% 
  mutate(city_state = fct_reorder(city_state, odds_ratio)) %>% 
  ggplot(aes(x = city_state, y = odds_ratio, color = odds_ratio)) +
  geom_point() +
  ylim(0, 5) +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper, width = .3)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
    labs(
    x = "Cities",
    y = "Adjusted odds ratio",
    title = "Odds Ratio of Solving Homicides in Major U.S. Cities Comparing Male to Female Victims")
or_plot
```

 * On the plot, we can see that most of the cities have odd ratio between 0 and 1 for solving homicides comparing male victims to female victims, which means that the odds of having a resolved homicide among male victims is lower than the odds of having a resolved homicide among female victims in those cities, adjusting for victim age and victim race. 
 
 * `New York, NY` has the lowest adjusted odds ratio, and `Albuquerque, MM` has the highest adjusted odds ratio.

 * `Fresno, CA`, `Stockton, CA` and `Albuquerque, NM` are the 3 cities with the highest adjusted ORs, the wide 95% CI showing there may be a high variability in these estimates rather than an effect of victim sex on solving homicides.
 
 
### Problem 3

#### Load and Tidy Data

```{r}
birthweight_data = read_csv("./data/birthweight.csv")

birthweight_data = birthweight_data %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
    )

```

There are `r sum(is.na(birthweight_data))` missing data, so we don't need to worry about that. 

#### Model 1 

```{r}
m1 = lm(bwt ~ wtgain + mheight, data = birthweight_data)

summary(m1) %>% 
  broom::tidy()

m1_plot = birthweight_data %>% 
  select(bwt, wtgain, mheight) %>% 
  modelr::add_residuals(m1) %>% 
  modelr::add_predictions(m1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_violin() +
  geom_point(alpha = 0.5)  +
  labs(title = "Predictions vs. Residuals",
       x = "Predictions", 
       y = "Residuals",) +
  theme(plot.title = element_text(hjust = 0.5))
  
m1_plot
```


* I picked the variable `wtgain` and `mheight` as the predictor for model 1 based on a hypothesized structure for the factors that underly birthweight. I think mother’s weight gain and height during pregnancy is closely related to baby's birthweight. 
* The `Prediction vs Residual` plot generated shows a big cluster of points around fitted values equal 2000 - 4000 where the model residuals tend to evenly distributed around 0.

#### Model 2 & Model 3

```{r}
m2 = lm(bwt ~ blength + gaweeks, data = birthweight_data)

summary(m2) %>% 
  broom::tidy()

m3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_data)

summary(m3) %>% 
  broom::tidy()
```

#### Croddvalidation 

```{r}
cv_df = crossv_mc(birthweight_data, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(m1_cv = map(train, ~lm(bwt ~ wtgain + mheight, data = .x)),
         m2_cv = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         m3_cv = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_m1 = map2_dbl(m1_cv, test, ~rmse(model = .x, data = .y)),
         rmse_m2 = map2_dbl(m2_cv, test, ~rmse(model = .x, data = .y)), 
         rmse_m3 = map2_dbl(m3_cv, test, ~rmse(model = .x, data = .y)))
```


```{r}

cv_plot = cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(everything(),
               names_to = "model",
               values_to = "rmse",
               names_prefix = "rmse_") %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs (
    title = "Cross Validation Comparisons",
    x = "Model",
    y = "RMSE"
  )

cv_plot
```


* From the plot, we can see that model 1 has the highest RMSE and model 3 has the lowest RMSE. 
* We should select model 3 as a better choice to predict birth weight of babies because the lower RMSE the better. 

